Image Caption Generation With CLIP+GPT-2 Model

### 2025-05-04 Latex_Paper/Paper.tex
update all

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{microtype}

\usepackage[margin=1in]{geometry}
\setlength{\parskip}{0.5em}
\setlength{\parindent}{0em}
\makeatletter
\def\@maketitle{
  \newpage
  \null
  \vskip 2em
  \begin{center}
  \let \footnote \thanks
    {\LARGE \@title \par}
    \vskip 1.5em
    {\large \lineskip .5em
      \begin{tabular}[t]{c}
        \@author
      \end{tabular}\par}
    \vskip 1em
    {\large \@date}
  \end{center}
  \par
  \vskip 1.5em}
\makeatother

@@

\textbf{Augmentation Pipeline:} SimCLR relies heavily on augmentations, which include:
\begin{itemize}
  \item Random crop and resize
  \item Color jittering
  \item Gaussian blur
  \item Horizontal flipping
\end{itemize}
\begin{equation}
    L = -\sum_{i \in I} \log \frac{\exp(\text{sim}(z_i, z_j)/\tau)}{\sum_{k \neq i}\exp(\text{sim}(z_i, z_k)/\tau)}
    \end{equation}
    where $\text{sim}(z_i, z_j)$ is the cosine similarity between embeddings, and $\tau$ is the temperature hyperparameter.

@@

    \bibitem{mokady2021clipcap}
    Mokady, R., Hertz, A., \& Bermano, A. H. (2021). ``ClipCap: CLIP Prefix for Image Captioning.'' arXiv preprint arXiv:2111.09734.

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{microtype}
% \usepackage{titlesec}
% \titleformat{\subsubsection}[runin]
%   {\normalfont\normalsize} 
%   {\thesubsubsection}      
%   {1em}                    
%   {}                     
%   []       
% \titlespacing*{\subsubsection}
%   {0pt}                       
%   {1.5ex plus 0.5ex minus 0.2ex} 
%   {0.8ex plus 0.2ex}                 
\usepackage{tikz}

\usetikzlibrary{shapes.geometric, arrows, positioning, fit, backgrounds}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage[margin=1in]{geometry}
\setlength{\parskip}{0.5em}
\setlength{\parindent}{0em}
\makeatletter
\def\@maketitle{
  \newpage
  \null
  \vskip 2em
  \begin{center}
  \let \footnote \thanks
    {\LARGE \@title \par}
    \vskip 1.5em
    {\large \lineskip .5em
      \begin{tabular}[t]{c}
        \@author
      \end{tabular}\par}
    \vskip 1em
    {\large \@date}
  \end{center}
  \par
  \vskip 1.5em}
\makeatother

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{figure1.png}
    \caption{CLIP+GPT-2 Training Pipeline}
    \label{fig:architecture}
    \end{figure}

\subsubsection{Data Set}

We utilize the MS COCO dataset \cite{COCO}for training and evaluation, 
MS COCO (Microsoft Common Objects in Context) 
is a large-scale image recognition, segmentation, 
and annotation dataset that is widely used in research 
in the field of computer vision, especially in tasks 
such as image captioning, object detection, and semantic 
segmentation. It contains 330K images with 5 captions each. 
We will split our dataset into three parts: 80\% training, 10\% validation, 10\% testing.

\subsubsection{ Data Preparation}
\begin{equation}
    L = -\sum_{i \in I} \log \frac{\exp(\text{sim}(z_i, z_j)/\tau)}{\sum_{k \neq i}\exp(\text{sim}(z_i, z_k)/\tau)}
    \end{equation}
    where $\text{sim}(z_i, z_j)$ is the cosine similarity between embeddings, and $\tau$ is the temperature hyperparameter.

@@

    \bibitem{COCO}
    Xinlei Chen, Hao Fang, Tsung-Yi Lin, Ramakrishna Vedantam, Saurabh Gupta, Piotr Dollár, and C Lawrence Zitnick. 2015. Microsoft coco captions: Data collection and evaluation server. arXiv preprint arXiv:1504.00325.
